---
title: "CP05 Random Forest"
author: "Camron Pearce"
date: "2024-06-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, include = TRUE)
```

## Tidying CP05 Data

```{r include=FALSE, echo=TRUE}
library(tidyverse)
library(cowplot)
library(tidymodels)
library(ggplot2)
library(knitr)
library(readxl)
library(corrplot)
library(ggthemes)
library(gridExtra)
library(gt)
library(gtExtras)
library(visdat)
library(fastDummies)
library(MASS)
library(glmnet)
library(ranger)
library(xgboost)
library(discrim)
library(doParallel)
library(themis)
library(kableExtra)
library(vip)
library(pROC)
library(tune)
library(gridExtra)
library(kknn)
library(yardstick)

tidymodels_prefer()
```



```{r tidying}
#formatting data like the heart failure data
#----------------------------------------

# Specify the file path of the Excel workbook
excel_file <- "CP05.xlsx"

# Define a vector of group definitions
group_identities <- list(c(1:4), c(5:8), c(9:12), c(13:16))

# Set the names of the resulting lists
# number of names must match the amount of lists generated in group_identities, each ""

group_names <- c("a", "b", "c", "d")

sheet_names <- excel_sheets(excel_file)

# Create a list to store the data frames
df_list <- lapply(sheet_names, function(sheet_name) read_excel(excel_file, sheet = sheet_name))

# Remove elements with names containing the word "Apnea"
df_list <- df_list[!grepl("Apnea", sheet_names)]


#function for summarizing each df by day collected

time_clean <- function(df) {
  df$Time <- as.Date(substr(df$Time, 1, 10), format = "%Y-%m-%d")
  df %>%
    group_by(Time) %>%
    select(-c(Tbody, Phase, Recording, Alarms, Rinx, RH, Tc, Comp))
}

df_list_clean <- lapply(df_list, time_clean)

#remove NAs
df_list_clean <- lapply(df_list_clean, function(df) df[complete.cases(df), ])

# Define a function to average all of the dataframes as defined by the number of group identities
merge_n <- function(df_list_clean, indices) {
  df_merged <- bind_rows(df_list_clean[indices])
  return(df_merged)
}

# Apply the merge_n function to the list
groups_merged <- lapply(group_identities, function(indices) merge_n(df_list_clean, indices))

# Rename columns for each data frame in the list
for (i in seq_along(groups_merged)) {
  df <- groups_merged[[i]]
  names(df)[-1] <- sub("Time_", "", names(df)[-1])
  groups_merged[[i]] <- df
}

#trying to combine by mouse group
# Merge the data frames within groups_merged and replace "Uninfected" with 0 and "Infected" with 1
big_merged <- groups_merged %>%
  bind_rows() 


big_merged_ac <- big_merged %>% 
  mutate(Time = ifelse(Time %in% unique(big_merged$Time)[1:4], "acute", "chronic"))


############
#Might need to remove this to re-run the models
big_merged <- big_merged %>% 
 mutate(wt = ifelse(grepl("WT", Subject), 1, ifelse(grepl("BEN", Subject), 0, NA)))




big_merged_ac$Subject <- as.factor(big_merged_ac$Subject)
big_merged_ac$Time <- factor(big_merged_ac$Time, levels = c("acute", "chronic"))

wt_df_ac <- big_merged_ac %>% 
  filter(grepl("WT", Subject))

benac_df_ac <- big_merged_ac %>% 
  filter(grepl("BENaC", Subject))

#splitting wt and benac - averaging for initial testing purposes

average_data <- big_merged %>% 
  group_by(Subject, Time) %>% 
  summarize_all(mean, na.rm = TRUE, .groups = "drop") %>% 
  ungroup() 

average_data_all <- average_data %>% 
  mutate(Status = ifelse(grepl("Uninfected", Subject), 0, ifelse(grepl("Infected", Subject), 1, NA)))
average_data_all$Status <- as.factor(average_data_all$Status)
average_data_all$Time <- as.Date(average_data_all$Time)


# Calculate the difference in days from the first date
average_data_all$Day <- as.numeric(difftime(average_data_all$Time, min(average_data_all$Time), units = "days")) + 1


average_data_ac <- average_data_all %>% 
  mutate(Time = ifelse(Time %in% unique(average_data$Time)[1:4], "acute", "chronic"))
average_data_ac$Status <- as.factor(average_data_ac$Status)
average_data_ac$Time <- factor(average_data_ac$Time, levels = c("acute", "chronic"))

#---------

wt_df_ac <- average_data_ac %>% 
  filter(grepl("WT", Subject))

benac_df_ac <- average_data_ac %>% 
  filter(grepl("BENaC", Subject))

#-----------------------
#beginning the process

#randomizing the wt_ac data
set.seed(7)
wt_ac <- wt_df_ac %>% 
  select(-Subject) %>% 
  sample_frac(1)

head(wt_ac)

##data forthe entire dataset
random_all <- average_data_ac %>% 
  select(-Subject) %>% 
  sample_frac(1)

```

Focusing only on wt data for training
```{r}
dim(random_all)
vis_dat(random_all)
```



```{r visualizing}
ggplot(random_all, aes(x = as.factor(Time), fill = "maroon")) + 
  geom_bar() + 
  scale_fill_manual(values = "maroon") +
  labs(title = "Distribution of Acute vs Chronic Timepoints", x = "Status", y = "Time") +
  theme(legend.position = "none")
```

## Variable Correlation Plots

```{r correlation}
infectioncorr <- random_all %>% 
  select(where(is.numeric)) %>% 
  cor() %>% 
  corrplot(order = "AOE", type = "lower", tl.col = "black")
```

## More data visualization

```{r}
ggplot(data = random_all, aes(x = f, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "Frequency across acute and chronic phase", x = "Frequency", fill = "Phase")

ggplot(data = random_all, aes(x = TVb, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "TVb across acute and chronic phase", x = "TVb", fill = "Phase")

ggplot(data = random_all, aes(x = Penh, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "Penh across acute and chronic phase", x = "Penh", fill = "Phase")

ggplot(data = random_all, aes(x = EF50, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "EF50 across acute and chronic phase", x = "EF50", fill = "Phase")

ggplot(data = random_all, aes(x = Ti, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "Ti across acute and chronic phase", x = "Ti", fill = "Phase")

ggplot(data = random_all, aes(x = Te, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "Te across acute and chronic phase", x = "Te", fill = "Phase")

#removed outliers here and scaled down, maybe consider for all
ggplot(data = random_all, aes(x = EIP, group = Time, fill = Time)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "EIP across acute and chronic phase", x = "EIP", fill = "Phase") +
  coord_cartesian(xlim = c(2,2.75))

ggplot(data = random_all, aes(x = EEP, group = Time, fill = Time)) +
  geom_boxplot() +
  scale_fill_manual(labels = c("Acute", "Chronic"), values = c("lightblue", "maroon")) +
  labs(title = "EEP across acute and chronic phase", x = "EEP", fill = "Phase")
```

## Splitting Data for modeling

Split into train and test

```{r}
set.seed(10)

random_all_split <- random_all %>% 
  initial_split(prop = 0.80, strata = "Status")

train_all <- training(random_all_split)
test_all <- testing(random_all_split)

dim(train_all)
dim(test_all)
```


### Building the random forest model

```{r}
wt_recipe <- recipe(Status ~ ., data = train_all) %>%
  step_dummy(all_nominal_predictors()) %>%   
  step_center(all_predictors()) %>% 
  step_scale(all_predictors()) %>%
  step_upsample(Status, over_ratio = 1)

prep(wt_recipe) %>%
  bake(new_data = train_all) %>%
  head() %>%
  kable() %>%
  kable_styling(full_width = F) %>%
  scroll_box(width = "100%", height = "200px")
```

### K-fold cross validation

```{r}

wt_folds <- vfold_cv(train_all, v = 10, strata = Status)

```

1. Parameters for tuning, mode and engine of Logistic Regression model
```{r}
#logistic regression
wt_log_reg <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")

#knn
wt_knn_mod <- nearest_neighbor(neighbors = tune()) %>% 
  set_engine("kknn") %>% 
  set_mode("classification")

#LDA
wt_lda_mod <- discrim_linear() %>% 
  set_engine("MASS") %>% 
  set_mode("classification")

#QDA
wt_qda_mod <- discrim_quad() %>% 
  set_engine("MASS") %>% 
  set_mode("classification")

#Elastic Net
wt_en_mod <- multinom_reg(mixture = tune(), penalty = tune()) %>% 
  set_engine("glmnet") %>% 
  set_mode("classification")

#rf
wt_rf_mod <- rand_forest(mtry = tune(), trees = tune(), min_n = tune()) %>%
  set_engine("ranger", importance = "impurity") %>%
  set_mode("classification")

#boosted trees
wt_bt_mod <- boost_tree(mtry = tune(), trees = tune(), learn_rate = tune()) %>% 
  set_engine("xgboost") %>% 
  set_mode("classification")
```

2. Workflow and model and recipe

```{r}

# Logistic Regression
wt_log_wkflow <- workflow() %>%
  add_model(wt_log_reg) %>%
  add_recipe(wt_recipe)


# KNN Model
wt_knn_wkflow <- workflow() %>%
  add_model(wt_knn_mod) %>%
  add_recipe(wt_recipe)

# LDA
wt_lda_wkflow <- workflow() %>%
  add_model(wt_lda_mod) %>%
  add_recipe(wt_recipe)

# QDA
wt_qda_wkflow <- workflow() %>%
  add_model(wt_qda_mod) %>%
  add_recipe(wt_recipe)

# Elastic Net
wt_en_wkflow <- workflow() %>%
  add_model(wt_en_mod) %>%
  add_recipe(wt_recipe)

# Random Forest
wt_rf_wkflow <- workflow() %>%
  add_model(wt_rf_mod) %>% 
  add_recipe(wt_recipe)

#Boosted Trees
wt_bt_wkflow <- workflow() %>%
  add_model(wt_bt_mod) %>%
  add_recipe(wt_recipe)
```

3. Tuning grid to set up range

```{r}

#knn model
wt_neighbors_grid <- grid_regular(neighbors(range = c(1, 20)), levels = 20)

#elastic net
wt_en_grid <- grid_regular(penalty(range = c(0.02, 3), trans = identity_trans()),
                           mixture(range = c(0,1)), levels = 10)

#random forest
wt_rf_grid <- grid_regular(mtry(range = c(1, 10)),
                              trees(range = c(50, 1000)),
                              min_n(range = c(5, 25)), levels = 10)

#boosted trees
wt_bt_grid <- grid_regular(mtry(range = c(1, 10)),
                           trees(range = c(100, 1000)),
                           learn_rate(range = c(-10, -1)),
                           levels = 5)

```

4. Actually tune to find best fit and save as rds file

*dont need to run this every time, just need the .rds file, i think*
```{r}
#knn
run_if <- function() {
  if (!file.exists("wt_knn_all.rds")) {
    registerDoParallel(cores = 6)
    
    wt_tune_res_knn <- tune_grid(
      object = wt_knn_wkflow,
      resamples = wt_folds,
      grid = wt_neighbors_grid
    )
    
    write_rds(wt_tune_res_knn, file = "wt_knn_all.rds")
  } else {
    message("File 'wt_knn_all.rds' already exists. Skipping the computation.")
  }
}

# Call the function to run the code and save if 'wt_rf.rds' doesn't exist
run_if()

#--------------------------------------

#knn
run_if <- function() {
  if (!file.exists("wt_en_all.rds")) {
    registerDoParallel(cores = 6)
    
    wt_tune_res_en <- tune_grid(
      object = wt_en_wkflow,
      resamples = wt_folds,
      grid = wt_en_grid
    )
    
    write_rds(wt_tune_res_en, file = "wt_en_all.rds")
  } else {
    message("File 'wt_en_all.rds' already exists. Skipping the computation.")
  }
}

# Call the function to run the code and save if 'wt_rf.rds' doesn't exist
run_if()

#------------------------------------------

#random forest tuning
run_if <- function() {
  if (!file.exists("wt_rf_all.rds")) {
    registerDoParallel(cores = 6)
    
    wt_tune_res_rf <- tune_grid(
      object = wt_rf_wkflow,
      resamples = wt_folds,
      grid = wt_rf_grid
    )
    
    write_rds(wt_tune_res_rf, file = "wt_rf_all.rds")
  } else {
    message("File 'wt_rf_all.rds' already exists. Skipping the computation.")
  }
}

# Call the function to run the code and save if 'wt_rf.rds' doesn't exist
run_if()

#--------------------------------------------

#knn
run_if <- function() {
  if (!file.exists("wt_bt_all.rds")) {
    registerDoParallel(cores = 6)
    
    wt_tune_res_bt <- tune_grid(
      object = wt_bt_wkflow,
      resamples = wt_folds,
      grid = wt_bt_grid
    )
    
    write_rds(wt_tune_res_bt, file = "wt_bt_all.rds")
  } else {
    message("File 'wt_bt_all.rds' already exists. Skipping the computation.")
  }
}

# Call the function to run the code and save if 'wt_rf.rds' doesn't exist
run_if()


```
5. load tuned model
```{r load}

#knn
wt_knn_tuned <- read_rds(file = "wt_knn_all.rds")

#en
wt_en_tuned <- read_rds(file = "wt_en_all.rds")

#random forest
wt_rf_tuned <- read_rds(file = "wt_rf_all.rds")

#boosted tree
wt_bt_tuned <- read_rds(file = "wt_bt_all.rds")

```

6. analyze performance
```{r}

#knn
best_knn <- show_best(wt_knn_tuned, metric = "roc_auc")

#en
best_en <- show_best(wt_en_tuned, metric = "roc_auc")

#ransom forest
best_rf <- show_best(wt_rf_tuned, metric = "roc_auc")

#boosted tree
best_bt <- show_best(wt_bt_tuned, metric = "roc_auc")


```
Figure shows efficacy of various random forest models.

## Evaluating the models

```{r}
#knn 
 p_knn <- autoplot(wt_knn_tuned) +
  theme_clean() + 
   theme(
     plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),   # Title
     axis.text.x = element_text(size = 10, angle = 45, hjust = 1),      # X-axis text
     axis.text.y = element_text(size = 10),                             # Y-axis text
     axis.title.x = element_text(size = 12, face = "bold"),             # X-axis title
     axis.title.y = element_text(size = 12, face = "bold")              # Y-axis title
   ) +
   labs(
     x = "# Nearest Neighbors",
     y = "Value",
     title = "Efficacy of K-Nearest Neighbor Models"  # Customize Plot Title
  )
p_knn

#en
p_en <- autoplot(wt_en_tuned, metric = "roc_auc") +
  theme_clean() + 
   theme(
     plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),   # Title
     axis.text.x = element_text(size = 10, angle = 45, hjust = 1),      # X-axis text
     axis.text.y = element_text(size = 10),                             # Y-axis text
     axis.title.x = element_text(size = 12, face = "bold"),             # X-axis title
     axis.title.y = element_text(size = 12, face = "bold")              # Y-axis title
   ) +
   labs(
     x = "Amount of Regularization",
     y = "ROC-AUC",
     title = "Efficacy of Elastic Net Models"  # Customize Plot Title
  )
p_en


#rf
p_rf <- autoplot(wt_rf_tuned, metric = "roc_auc") +
  theme_bw() +
   theme(
     plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),   # Title
     axis.text.x = element_text(size = 10, angle = 45, hjust = 1),      # X-axis text
     axis.text.y = element_text(size = 10),                             # Y-axis text
     axis.title.x = element_text(size = 12, face = "bold"),             # X-axis title
     axis.title.y = element_text(size = 12, face = "bold")              # Y-axis title
   ) +
   labs(
     x = "# of Randomly Selected Predictors",
     y = "ROC-AUC",
     title = "Efficacy of Random Forest Models"  # Customize Plot Title
  )
p_rf

#boosted tree
p_bt <- autoplot(wt_bt_tuned, metric = "roc_auc") +
  theme_bw() +
   theme(
     plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),   # Title
     axis.text.x = element_text(size = 10, angle = 45, hjust = 1),      # X-axis text
     axis.text.y = element_text(size = 10),                             # Y-axis text
     axis.title.x = element_text(size = 12, face = "bold"),             # X-axis title
     axis.title.y = element_text(size = 12, face = "bold")              # Y-axis title
   ) +
   labs(
     x = "# of Randomly Selected Predictors",
     y = "ROC-AUC",
     title = "Efficacy of Boosted Tree Models"  # Customize Plot Title
  )
p_bt
```

## Select the model and apply it to the workflow
```{r}
#KNN
best_wt_neighbors <- select_best(wt_knn_tuned, metric = "roc_auc")
final_wt_knn_model <- finalize_workflow(wt_knn_wkflow, best_wt_neighbors)

#en
best_wt_en <- select_best(wt_en_tuned, metric = "roc_auc")
final_wt_en_model <- finalize_workflow(wt_en_wkflow, best_wt_en)

#RF
best_wt_rf <- select_best(wt_rf_tuned, metric = "roc_auc")
final_wt_rf_model <- finalize_workflow(wt_rf_wkflow, best_wt_rf)

#boosted tree
best_wt_bt <- select_best(wt_bt_tuned, metric = "roc_auc")

final_wt_bt_model <- finalize_workflow(wt_bt_wkflow, best_wt_bt)


```

## Fitting ALL the models together
```{r}
#fit models together

#Log reg
wt_log_fit <- fit(wt_log_wkflow, train_all)

#knn
wt_knn_fit <- fit(final_wt_knn_model, train_all)

#lda
wt_lda_fit <- fit(wt_lda_wkflow, train_all)

#qda
wt_qda_fit <- fit(wt_qda_wkflow, train_all)

#en
wt_en_fit <- fit(final_wt_en_model, train_all)

#rf
wt_rf_fit <- fit(final_wt_rf_model, train_all)

#bt
wt_bt_fit <- fit(final_wt_bt_model, train_all)
```

## ROC_AUC from train_all data

```{r}

#log regression
wt_log_train_results_1 <- augment(wt_log_fit, new_data = train_all)
predictions_log <- select(wt_log_train_results_1, .pred_1, Status)
truth_log <- as.numeric(as.character(predictions_log$Status))

wt_log_train_results <- auc(roc(truth_log, predictions_log$.pred_1))

#knn
wt_knn_train_results_1 <- augment(wt_knn_fit, new_data = train_all)
predictions_knn <- select(wt_knn_train_results_1, .pred_1, Status)
truth_knn <- as.numeric(as.character(predictions_knn$Status))

wt_knn_train_results <- auc(roc(truth_knn, predictions_knn$.pred_1))

#lda
wt_lda_train_results_1 <- augment(wt_lda_fit, new_data = train_all)
predictions_lda <- select(wt_lda_train_results_1, .pred_1, Status)
truth_lda <- as.numeric(as.character(predictions_lda$Status))

wt_lda_train_results <- auc(roc(truth_lda, predictions_lda$.pred_1))

#qda
wt_qda_train_results_1 <- augment(wt_qda_fit, new_data = train_all) 
predictions_qda <- select(wt_qda_train_results_1, .pred_1, Status)
truth_qda <- as.numeric(as.character(predictions_qda$Status))

wt_qda_train_results <- auc(roc(truth_qda, predictions_qda$.pred_1))

#en
wt_en_train_results_1 <- augment(wt_en_fit, new_data = train_all)
predictions_en <- select(wt_en_train_results_1, .pred_1, Status)
truth_en <- as.numeric(as.character(predictions_en$Status))

wt_en_train_results <- auc(roc(truth_en, predictions_en$.pred_1))

#rf
wt_rf_train_results1 <- augment(wt_rf_fit, new_data = train_all) 
predictions_rf <- select(wt_rf_train_results1, .pred_1, Status)
truth_rf <- as.numeric(as.character(predictions_rf$Status))

wt_rf_train_results <- auc(roc(truth_rf, predictions_rf$.pred_1))

#bt
wt_bt_train1_results_1 <- augment(wt_bt_fit, new_data = train_all)
predictions_bt <- select(wt_bt_train_results_1, .pred_1, Status)
truth_bt <- as.numeric(as.character(predictions_bt$Status))

wt_bt_train_results <- auc(roc(truth_bt, predictions_bt$.pred_1))

```

## AUC-ROC values for each model

```{r}
wt_models <- c("Logistic Regression", "K-Nearest Neighbor", "Linear Discrimination Analysis", "Quadratic Discriminant Analysis", "Elastic Net", "Random Forest", "Gradient-Boosted Trees")

wt_models_roc_auc <- c(wt_log_train_results,
                       wt_knn_train_results,
                       wt_lda_train_results,
                       wt_qda_train_results,
                        wt_en_train_results,
                        wt_rf_train_results,
                        wt_bt_train_results
                       )

wt_training_results <- tibble(Model = wt_models, ROC_AUC = wt_models_roc_auc) %>% 
  arrange(-wt_models_roc_auc) %>% 
  gt() %>% 
  tab_header(title = "Predicting Infection Status: AUC-ROC Values") %>% 
  gt_theme_nytimes() %>% 
  cols_label(ROC_AUC = "ROC-AUC")

wt_training_results

```

#----------------------------------------------------------------------

## Test Data

```{r}

#log regression
wt_log_test_results_1 <- augment(wt_log_fit, new_data = test_all)
predictions_test_log <- select(wt_log_test_results_1, .pred_1, Status)
truth_test_log <- as.numeric(as.character(predictions_test_log$Status))

wt_log_test_results <- auc(roc(truth_test_log, predictions_test_log$.pred_1))
wt_log_accuracy <- augment(wt_log_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)


#knn
wt_knn_test_results_1 <- augment(wt_knn_fit, new_data = test_all)
predictions_test_knn <- select(wt_knn_test_results_1, .pred_1, Status)
truth_test_knn <- as.numeric(as.character(predictions_test_knn$Status))

wt_knn_test_results <- auc(roc(truth_test_knn, predictions_test_knn$.pred_1))
wt_knn_accuracy <- augment(wt_knn_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#lda
wt_lda_test_results_1 <- augment(wt_lda_fit, new_data = test_all)
predictions_test_lda <- select(wt_lda_test_results_1, .pred_1, Status)
truth_test_lda <- as.numeric(as.character(predictions_test_lda$Status))

wt_lda_test_results <- auc(roc(truth_test_lda, predictions_test_lda$.pred_1))
wt_lda_accuracy <- augment(wt_lda_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#qda
wt_qda_test_results_1 <- augment(wt_qda_fit, new_data = test_all)
predictions_test_qda <- select(wt_qda_test_results_1, .pred_1, Status)
truth_test_qda <- as.numeric(as.character(predictions_test_qda$Status))

wt_qda_test_results <- auc(roc(truth_test_qda, predictions_test_qda$.pred_1))
wt_qda_accuracy <- augment(wt_qda_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#en
wt_en_test_results_1 <- augment(wt_en_fit, new_data = test_all)
predictions_test_en <- select(wt_en_test_results_1, .pred_1, Status)
truth_test_en <- as.numeric(as.character(predictions_test_en$Status))

wt_en_test_results <- auc(roc(truth_test_en, predictions_test_en$.pred_1))
wt_en_accuracy <- augment(wt_en_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#rf
wt_rf_test_results_1 <- augment(wt_rf_fit, new_data = test_all)
predictions_test_rf <- select(wt_rf_test_results_1, .pred_1, Status)
truth_test_rf <- as.numeric(as.character(predictions_test_rf$Status))

wt_rf_test_results <- auc(roc(truth_test_rf, predictions_test_rf$.pred_1))
wt_rf_accuracy <- augment(wt_rf_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#bt
wt_bt_test1_results_1 <- augment(wt_bt_fit, new_data = test_all)
predictions_test_bt <- select(wt_bt_test_results_1, .pred_1, Status)
truth_test_bt <- as.numeric(as.character(predictions_test_bt$Status))

wt_bt_test_results <- auc(roc(truth_test_bt, predictions_test_bt$.pred_1))
wt_bt_accuracy <- augment(wt_bt_fit, new_data = test_all) %>% 
  accuracy(Status, estimate = .pred_class)

#-----------------

wt_models_test <- c("Random Forest", "Gradient-Boosted Trees", "K-Nearest Neighbor", "Quadratic Discriminant Analysis", "Elastic Net", "Logistic Regression",  "Linear Discrimination Analysis")

tibble(Model = wt_models_test, ROC_AUC = c(wt_rf_test_results,
                                      wt_bt_test_results,
                                      wt_knn_test_results,
                                      wt_qda_test_results,
                                      wt_en_test_results,
                                      wt_log_test_results,
                                      wt_lda_test_results
                                     
                                     
                                     ), 
       Accuracy = c(wt_rf_accuracy$.estimate,
                    wt_bt_accuracy$.estimate,
                    wt_knn_accuracy$.estimate,
                    wt_qda_accuracy$.estimate,
                    wt_en_accuracy$.estimate,
                    wt_log_accuracy$.estimate,
                    wt_lda_accuracy$.estimate
                    
                    
                    )) %>% 
  gt() %>% 
  tab_header(title = "Performance Metrics of Tested Models") %>% 
  gt_theme_nytimes()

```

Looking at a confusion matrix
```{r}
final_log_model_test <- augment(wt_log_fit, test_all)
final_knn_model_test <- augment(wt_knn_fit, test_all)
final_lda_model_test <- augment(wt_lda_fit, test_all)
final_qda_model_test <- augment(wt_qda_fit, test_all)
final_en_model_test <- augment(wt_en_fit, test_all)
final_rf_model_test <- augment(wt_rf_fit, test_all)
final_bt_model_test <- augment(wt_bt_fit, test_all)

conf_mat(final_rf_model_test, truth = Status, .pred_class) %>% 
  autoplot(type = "heatmap")

```


## All conf matrix in one facet

```{r}
# List of final model fit objects
final_model_fits <- list(wt_log_fit, 
                         wt_knn_fit, 
                         wt_lda_fit, 
                         wt_qda_fit, 
                         wt_en_fit, 
                         wt_rf_fit, 
                         wt_bt_fit)

# List of model names
model_names <- c("LOG", 
                 "KNN", 
                 "LDA", 
                 "QDA", 
                 "EN", 
                 "RF", 
                 "BT")

# Create confusion matrix plots for each model
confusion_plots <- lapply(seq_along(final_model_fits), function(i) {
  final_model_test <- augment(final_model_fits[[i]], new_data = test_all)
  conf_mat(final_model_test, truth = Status, .pred_class) %>% 
    autoplot(type = "heatmap") +
    ggtitle(model_names[i]) +
    theme(
      plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Larger and bold title
      text = element_text(face = "bold", size = 6),                     # Bold and larger numbers
      axis.text = element_text(size = 10),                              # Larger axis values (0 and 1)
      axis.title = element_text(size = 12, face = "bold")               # Larger and bold axis titles
    )
})

# Arrange the confusion matrix plots in a grid
grid.arrange(grobs = confusion_plots, ncol = 4)

```


Plotting the ROC Curve

```{r}
# List of final models
final_models <- list(wt_log_fit, 
                     wt_knn_fit, 
                     wt_lda_fit, 
                     wt_qda_fit, 
                     wt_en_fit, 
                     wt_rf_fit, 
                     wt_bt_fit)

# List of titles corresponding to each model
titles <- c("LOG", 
            "KNN", 
            "LDA", 
            "QDA", 
            "EN", 
            "RF", 
            "BT")


# Create plots individually with centered titles and capitalized axis labels
plots_list <- lapply(seq_along(final_models), function(i) {
  p <- augment(final_models[[i]], new_data = test_all) %>% 
    roc_curve(truth = Status, .pred_1) %>% 
    autoplot() +
    ggtitle(titles[i]) +
    theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), # Larger and bold title
      text = element_text(face = "bold", size = 6),                     # Bold and larger numbers
      axis.text.x = element_text(size = 10, angle = 45, hjust = 1),
      axis.text.y = element_text(size = 10),# Larger axis values (0 and 1)
      axis.title = element_text(size = 10, face = "bold"))+
    labs(x = "Specificity", y = "Sensitivity") # Set the axis titles
  return(p)
})

# Arrange plots in a grid
grid.arrange(grobs = plots_list, ncol = 4)


```

## Variable importance Plotting

```{r}

log_vip <- wt_log_fit %>% 
  extract_fit_engine() %>% 
  vip(aesthetics = list(fill = "maroon", color = "black")) +
  ggtitle("Logistic Regression VIP")

en_vip <- wt_en_fit %>% 
  extract_fit_engine() %>% 
  vip(aesthetics = list(fill = "maroon", color = "black")) +
  ggtitle("Elastic Net VIP")

rf_vip <- wt_rf_fit %>% 
  extract_fit_engine() %>% 
  vip(aesthetics = list(fill = "maroon", color = "black")) +
  ggtitle("Random Forest VIP")

bt_vip <- wt_bt_fit %>% 
  extract_fit_engine() %>% 
  vip(aesthetics = list(fill = "maroon", color = "black")) + 
  ggtitle("Boosted Trees VIP")


plot_grid(log_vip, en_vip, rf_vip, bt_vip, nrow = 2)
```
